DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-26 ase2017/paper.tex
Added LOC to implementation
Added description of LOC in the various modules of our implementation.

\textcolor{red}{Pascal: May I ask you to briefly mention the modules and also the LOC associated to each module? The tool paper reviewers usually like to know about the tool's complexity (i.e., number of modules/components and LOC).}

>>>>

The entire implementation consists of $400$ lines of MATLAB scripts for the UI
module, $585$ and $800$ lines of C code in the naive and abstract accelerator
model respectively.  $4000$ lines of C code for utility functions such as
interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
control synthesis module in CEGIS CBMC.  We evaluate \tool using $20$ regression
test cases.
